Checkpoint 4

### 2020-04-30 Checkpoint 4.Rmd

prediction_summary(y = Finaldata$ChinaVirusInterest,
  yrep = pred_1)
```

```{r}
### For predicting one case 
new_FL <- data.frame(Day = 7 , State = "FL") #Doesn't recognize state

set.seed(454)
pred_FL <- posterior_predict(
  model_100,
  newdata = new_FL)

pred_100 <- data.frame(y_new = pred_100[-1])

ggplot(pred_100, aes(x=y_new))+geom_density()

summary(pred_100)

@@

```{r}
#set.seed(454)
my_data <- data.frame(StateColor = "blue", State = "FL", Day = 18336)

# Simulate a set of predictions for each case in newdata
my_prediction <- posterior_predict(
 model_5,
  newdata = my_data)

>>>>

# pred_5 <- posterior_predict(
#   model_5,
#   newdata = Finaldata, transform = TRUE)

prediction_summary(y = Finaldata$ChinaVirusInterest,
  yrep = pred_1)

# prediction_summary(y = Finaldata$ChinaVirusInterest,
#   yrep = pred_5)
```

```{r}
### For predicting one case 
new_CA <- Finaldata%>% 
          filter(State=="CA") #filter the row of interest

set.seed(454)
pred_CA <- posterior_predict(
  model_100,
  newdata = new_CA)

pred_2 <- data.frame(y_new = pred_CA[-1])

ggplot(pred_2, aes(x=y_new))+geom_density()

summary(pred_2)

@@

```{r}
#set.seed(454)
my_data <- data.frame(StateColor = "blue", State = "FL", Day = 18336)
# Simulate a set of predictions for each case in newdata
#my_prediction <- posterior_predict(
 # model_5, 
  #newdata = my_data)

#my_prediction <- data.frame(y_new = my_prediction[,1])

#ggplot(my_prediction, aes(x = y_new)) + 
 # geom_density()

#summary(my_prediction)
```
